Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-04-26 scnn.tex
end of the day

In the classical 2-dimenstional convolution, each pixel is connected with the
same weight to its 4 closest neighbors. We use a graph to generalize this to the
irregular sphear sampling. From the ubiquitous HealPix
sampling~\citep{gorski2005healpix}, we create a weighted undirected graph where
each pixel is a node (vertex) that is connected to his $8$ or $7$ closest
neighbors.\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well
defined.} Given the set of nearest neighbors, we define the weight matrix $W$
using the following scheme
\begin{equation}
W[i,j]=\begin{cases}
e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}
Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected
pixels $i$ and $j$. The degree of a node (or a pixel) is defined as $d_i =
\sum_j W[i,j]$. The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$. 
An example of the resulting graph is displayed in Figure~\ref{fig:healpix_graph_4}.

>>>>

In the classical 2-dimenstional convolution, each pixel is connected with the
same weight to its 4 closest neighbors. We use a weighted undirected graph to
generalize this idea to the ubiquitous HealPix
sampling~\citep{gorski2005healpix}.  Each pixel is represented by a node
(vertex) connected to his $8$ or $7$ closest neighbors.\footnote{For some
pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of
nearest neighbors, we define the weight matrix $W$ using the following scheme
\begin{equation}
W[i,j]=\begin{cases}
e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}
Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected
pixels $i$ and $j$. This weighting scheme is important as the distances between
pixels varries du to the small sampling irregularities. Some of the
irregularities have been highlighted in the graph displayed in
Figure~\ref{fig:healpix_graph_4}.

These small irregularities are important as they prevent our approach to be affect slightly the degree of a node (or a pixel), defined as $d_i =
\sum_j W[i,j]$. The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$.
